### 2017-08-02 src/4_OnlineLearning.tex
Complexity of the hypothesis space

%=======================HASTA ACA REVISADO PROFE =========================
\subsection{Learning algorithms}
In all learning algorithms that are trained from example data, there is a
tradeoff between three factors \cite{dietterich2003}:
\begin{description}
\item[Complexity or capacity of the hypothesis class] 
 can be measured by the Vapnik\-Chervonenkis (VC) dimension

for best generalisation, we should
adjust the complexity of the learner model $\hat{f}$ o the complexity of the
data.

In polynomial regression, the complexity parameter is the order of the fitted polynomial, and
therefore we need to find a way to choose the best order that minimises the
generalisation error, that is, tune the complexity of the model to best fit the
complexity of the function inherent in the data.

The complexity of a learning problem mostly depends on the number of
training examples and the size of the searched hypothesis space.

>>>>

%=======================HASTA ACA REVISADO PROFE =========================
\subsection{Learning algorithms}
In all learning algorithms that are trained from example data, there is a
tradeoff between three factors \cite{dietterich2003}:
\begin{description}
\item[Complexity or capacity of the hypothesis class] is defined in terms of the
Vapnik-Chervonenkis (VC) dimension, which corresponds to the number of training
points that can be classified exactly by the hypothesis space. More formally,
the VC dimension of the hypothesis space $\mathcal{H}$ defined over instance
space $X$ is the size of the largest finite subset of $X$ shattered by
$\mathcal{H}$. The dataset $S$ is shattered by hypothesis space $\mathcal{H}$ if
and only if for every dichotomy of $S$ there exists some hypothesis in
$\mathcal{H}$ consistent with this dichotomy. A dichotomy of a set $S$ is a
partition of $S$ into two disjoint subsets \cite{vapnik2013nature}.

For example, the VC dimension of the lines in the plane is explained in figure
\ref{fig:vcdimension}:

\begin{figure}[!h]
  \centering
  \includegraphics[width=0.8\textwidth]{img/VCdimension}
  \caption{VC dimension example from \cite{vapnik2013nature}. The left figure
  shows that three vectors can be shattered by a line in a plane. However, if we
  add an extra vector $z_4$, it is impossible to shatter them with a
  plane.Therefore, linear classifiers has VC dimension equals to $d+1$ where $d$
  is the dimension of the instance space $X$.}
  \label{fig:vcdimension}
\end{figure}
